Visit Scotland Analysis

### 2023-06-21 visit_scotland_analysis.Rmd
Minor Plot Labelling Updates

dom_int_summary %>% 
  ggplot() +
  geom_line(aes(x = year, y = visits, colour = dom_int),
          size = 2) +
  geom_point(aes(x = year, y = visits, colour = dom_int), 
             size = 4) +
  ylim(0, 15000) +
  labs(x = "\n Year",
       y = "Visitors (Thousands) \n",
       title = "Annual Visits",
       subtitle = "Domestic & International Overnight Vistors",
       colour = "") +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  scale_colour_manual(values = c("Domestic" = "#540453",
                                 "International" = "#9fd6f3")) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

@@

dom_int_summary %>% 
  ggplot() +
  geom_line(aes(x = year, y = spend, colour = dom_int),
          size = 2) +
  geom_point(aes(x = year, y = spend, colour = dom_int), 
             size = 4) +
  ylim(0, 4000) +
  labs(x = "\n Year",
       y = "Expenditure (Million GBP) \n",
       title = "Annual Expenditure",
       subtitle = "Domestic & International Overnight Vistors",
       colour = "") +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  scale_colour_manual(values = c("Domestic" = "#540453",
                                 "International" = "#9fd6f3")) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

>>>>

dom_int_summary %>% 
  ggplot() +
  geom_line(aes(x = year, y = visits, colour = dom_int),
          size = 2) +
  geom_point(aes(x = year, y = visits, colour = dom_int), 
             size = 4) +
  ylim(0, 15000) +
  labs(x = "\n Year",
       y = "Visitors (Thousands) \n",
       title = "Annual Visits",
       subtitle = "Domestic & International Overnight Vistors (2009-2019)",
       colour = "") +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  scale_colour_manual(values = c("Domestic" = "#540453",
                                 "International" = "#9fd6f3")) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))

@@

dom_int_summary %>% 
  ggplot() +
  geom_line(aes(x = year, y = spend, colour = dom_int),
          size = 2) +
  geom_point(aes(x = year, y = spend, colour = dom_int), 
             size = 4) +
  ylim(0, 4000) +
  labs(x = "\n Year",
       y = "Expenditure (Million GBP) \n",
       title = "Annual Expenditure",
       subtitle = "Domestic & International Overnight Vistors (2009-2019)",
       colour = "") +
  scale_x_continuous(breaks = c(2009, 2010, 2011, 2012, 2013, 2014, 2015, 2016, 2017, 2018, 2019)) +
  scale_colour_manual(values = c("Domestic" = "#540453",
                                 "International" = "#9fd6f3")) +
  theme(plot.title = element_text(size = 15, face = "bold"),
        plot.subtitle = element_text(size = 10),
        panel.background = element_rect(fill = "white"),
        panel.grid = element_line(colour = "grey90", 
                                  linetype = "dashed"))
